Self Regulation Ontology Retest Analyses

### 2018-05-02 code/SRO_Retest_Analyses.Rmd
added new intratrial analyses

```{r}
boot_df %>%
  select(dv, p_time, task, pearson) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task),
            mean_pearson = mean(pearson))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  arrange(mean_pearson) %>%

@@

write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
```

@@

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
t1_dvs = t1_dvs %>% select(-X) 
t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
t2_dvs = t2_dvs %>% select(-X)

t1_dvs = t1_dvs %>% mutate(sub_id = as.character(sub_id))
t2_dvs = t2_dvs %>% mutate(sub_id = as.character(sub_id))

unique(t2_dvs$sub_id)

t1_dvs[,c("acc","sub_id", "breaks")] %>%
  left_join(t2_dvs[,c("acc","sub_id", "breaks")], by = c("sub_id", "breaks")) %>%
  distinct()
```

@@

```{r warning=FALSE, message=FALSE}
trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))

>>>>

```{r}
boot_df %>%
  select(dv, p_time, task, pearson) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task),
            mean_pearson = mean(pearson))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  arrange(mean_pearson)

@@

# write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
```

@@

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))

t1_dvs = t1_dvs %>% select(-X)
t2_dvs = t2_dvs %>% select(-X)
```

@@

```{r warning=FALSE, message=FALSE}
# trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
